An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-22 indicators/paper/supplement.Rmd
Remove supplement placeholders

<!-- Comment out or remove this line before generating final copy for submission; this will also remove the warning re: "Consecutive odd pages found". -->
\instructionspage

@@

\SItext

All our text goes here. Reference figures with the R chuck label as Figure~\ref{fig:fcast-finalized}.

All figures go on their own page after all of the text...

Edit `pnas-suppl-template.tex` for the correct Author list and Title.

@@

## Consider only state-like jurisdictions for which all signals of interest have at least 50 rows:
hosp_geo_values = unique(df_hospitalizations$geo_value)
for (i in seq_along(HOSP_SIGNALS)) {
  hosp_geo_values = intersect(hosp_geo_values, df_hosp_signals[[i]] %>% count(geo_value) %>% filter(n > 50) %>% pull(geo_value))
}

cat('Number of unique jurisdictions included in correlation analysis below:\n')
length(hosp_geo_values)
```

@@

for (i in seq_along(HOSP_SIGNALS)) {
  hosp_common_instances <- inner_join(hosp_common_instances,
                                      select(df_hosp_signals[[i]], geo_value, time_value),
                                      by=c("geo_value","time_value"))
}

cat('Number of common instances among all signals of interest in correlation analysis below:\n')
nrow(hosp_common_instances)
```

>>>>

<!-- Comment out or remove this line before generating final copy for submission; this will also remove the warning re: "Consecutive odd pages found". -->

@@

@@

## Consider only state-like jurisdictions for which all signals of interest have at least 50 rows:
hosp_geo_values = unique(df_hospitalizations$geo_value)
for (i in seq_along(HOSP_SIGNALS)) {
  hosp_geo_values = intersect(hosp_geo_values, df_hosp_signals[[i]] %>% count(geo_value) %>% filter(n > 50) %>% pull(geo_value))
}
```

@@

for (i in seq_along(HOSP_SIGNALS)) {
  hosp_common_instances <- inner_join(hosp_common_instances,
                                      select(df_hosp_signals[[i]], geo_value, time_value),
                                      by=c("geo_value","time_value"))
}
```
